A Journey from Wild to Textbook Data to Reproducibly Refresh the Wages Data from the National Longitudinal Survey of Youth Database

### 2022-02-18 paper/paper.Rmd
Added list of variables in Recap section.

It is worth noting that `gender` comes from a variable called `sex` in the database. We use the term `gender` as the reports about the data on various pages in the website more commnly use `gender`. Gender, as provided in the data, is self-reported and only has two categories, "male" and "female". The interchangeable use of these terms reflects that gender and sex are sometimes regarded as similar in surveys, although they are not. Measuring gender as a binary variable has the potential to fail to capture people who do not identify themselves as either male or female or people whose gender does not align with their sex classification [@kennedy2020using]. From a statistical perspective, this sometimes difficult the adjustment of survey statistics to the population when gender is measured, for example, with three categories, and the census measured it with only two categories and used the term sex [@kennedy2020using]. Hence, for modern societal studies, it is highly recommended to separate sex and gender in the survey question and provide more options to respond to questions on gender. This discourse should also be emphasized in teaching that using these two variables should be accompanied by special attention. Similar this also relates to race, as reported in the database. When doing an analysis with this variable, one should keep in mind that the purpose is to study racism rather than race.

@@

>>>>

For `gender` and `race`, we only rename the column names provided in `new_data_qnames`. It is worth noting that `gender` comes from a variable called `sex` in the database. We use the term `gender` as the reports on the data on the website typically use `gender`. Gender, as provided in the data, is self-reported and only has two categories, "male" and "female". The interchangeable use of these terms reflects that gender and sex are sometimes regarded as similar in surveys, although they are not. Measuring gender as a binary variable has the potential to fail to capture people who do not identify themself as either male or female or people whose gender does not align with their sex classification [@kennedy2020using]. From a statistical perspective, this sometimes difficult the adjustment of survey statistics to the population when gender is measured, for example, with three categories, and the census measured it with only two categories and used the term sex [@kennedy2020using]. Hence, nowadays, it is highly recommended to separate sex and gender in the survey question and provide more options to respond to questions on gender. This discourse should also be emphasized in teaching that using these two variables should be accompanied by special attention. Similar case to race, as reported in the database. When doing an analysis with this variable, one should keep in mind that the purpose is to study racism rather than race.

@@

In addition, the list of variables that we cover in those three datasets are as follows:

**`demog_nlsy79`** :

  1. `id`: A unique individual's ID number.
  2. `age_1979`: The age of the individual in 1979.
  3. `gender`: Gender of the individual, FEMALE and MALE.
  4. `race` : Race of the individual, NON-BLACK,NON-HISPANIC; HISPANIC; BLACK.
  5. `hgc`: The highest grade completed.
  6. `hgc_i`: Integer value of the highest grade completed.
  7. `ged`: Wether the respondent had a high school diploma or Graduate Equivalency Degree (GED). 1: High school diploma; 2: GED; 3: Both.

**`wages`** and its subset for high school dropouts cohort **`wages_hs_do`**:

  1. `id`: A unique individual's ID number. This is the `key` of the data as we saved the data as a `tsibble` object. 
  2. `year`: The year the observation was taken. This is the `index` of the data.
  3. `wage`: The mean of the hourly wages the individual gets at each of their different jobs. The value could be a weighted or an arithmetic mean. The weighted mean is used when the information of hours of work as the weight is available. The mean hourly wage could also be a predicted value if the original value is considered influential by the robust linear regression as part of data cleaning.
  4. `age_1979`: The age of the individual in 1979.
  5. `gender`: Gender of the individual: FEMALE and MALE.
  6. `race`: Race where the individual belongs to: NON-BLACK,NON-HISPANIC; HISPANIC; BLACK.
  7. `hgc`: The highest grade completed ever.
  8. `hgc_i`: Integer value of the highest grade completed ever.
  9. `grade`: Integer value of the highest grade completed corresponding to `year`. 
  10. `ged`: Wether the respondent had a high school diploma or Graduate Equivalency Degree (GED). 1: High school diploma; 2: GED; 3: Both.
  11. `njobs`: Number of jobs that an individual has.
  12. `hours:`: The total number of hours the individual usually works per week.
  13. `stwork`: The year when the individual starting to work.
  14. `yr_wforce`: The length of time in the workforce in years (`year` - `stwork`).
  15. `exp`: Work experience, i.e., the number of years of working. 
  16. `is_wm`: Whether the mean hourly wage is weighted mean, using the hour work as the weight, or regular/arithmetic mean. TRUE = is weighted mean. FALSE = is regular mean.
  17. `is_pred`: Whether the mean hourly wage is a predicted value of RLM or not.
